%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------
\documentclass{resume} % Use the custom resume.cls style
\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins

\usepackage{bibentry}
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}}
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\def\changemargin#1{\list{}{\leftmargin#1}\item[]}
\let\endchangemargin=\endlist 

\newcounter{qcounter}


%----------------------------------------------------------------------------------------
%	CONTACT SECTION
%----------------------------------------------------------------------------------------
\name{Lening Li} % Your name
\address{39 William St, Apt 203, Worcester, MA 01609 USA} % Your address
\address{+1~(774)~823~2639 \\ {lli4@wpi.edu} \\ \url{https://lening.li} \\ \url{https://github.com/leelening}}

\begin{document}

%----------------------------------------------------------------------------------------
%	REFERENCES SECTION
%----------------------------------------------------------------------------------------
\nobibliography{refs}
\bibliographystyle{ieeetr}

%----------------------------------------------------------------------------------------
%	RESEARCH INTERESTS SECTION
%----------------------------------------------------------------------------------------
\begin{rSection}{Research Interests}
    Reinforcement Learning \, $\circ$ \, Stochastic Optimal Control \, $\circ$ \, Game Theory \, $\circ$ \, Formal Methods
\end{rSection}


%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------
\begin{rSection}{Education}
{\bf Ph.D. Candidate in Robotics Engineering} \hfill {Aug. 2016 - Aug. 2021 (Exp.)} 
\\ {\it Worcester Polytechnic Institute (WPI)} \hfill {Worcester, MA USA} 
\\ {Overall GPA: \bf{4.0}/4.0}

{\bf M.S. in Robotics Engineering} \hfill {Aug. 2016 - May. 2021}
\\ {\it Worcester Polytechnic Institute (WPI)} \hfill {Worcester, MA USA} 
\\ {Overall GPA: \bf{3.70}/4.0}

{\bf M.S. in Computer Science} \hfill {Aug. 2014 - May 2016}
\\ {\it Worcester Polytechnic Institute (WPI)} \hfill {Worcester, MA USA} 
\\ {Overall GPA: \bf{3.64}/4.0}

{\bf B.S. in Computer Science \& B.A. in English Language and Literature} \hfill{Sep. 2010 - Jul. 2014}
\\ {\it Harbin Institute of Technology (HIT)} \hfill {China} 
\\ {Overall GPA: 85/100} ({\bf Top 10\%})
\end{rSection}

\begin{rSection}{Certifications}
{\bf Certification in College Teaching} \hfill {Jun. 2017 - Aug. 2019}
\\ {\it Higher Education Consortium of Central Massachusetts (HECCMA)} \hfill {Worcester, MA USA} 
\\ {Professional training on the teaching methods for providing high-quality courses.}

{\bf Certification in Fundamentals of Website Development} \hfill {Jun. 2015 - Aug. 2015}
\\ {\it Harvard Extension School} \hfill {Cambridge, MA USA}
\\ {Course covering ideology and methodology of website development, including CSS, HTML, JavaScript.}
\end{rSection}

%----------------------------------------------------------------------------------------
%	REPRESENTATIVE PROJECTS SECTION
%----------------------------------------------------------------------------------------
\begin{rSection}{Representative Projects}
    \begin{rSubsection}{Learning-based Planning with Temporal Logic Constraints}{Aug. 2016 - Present}{Researcher}{Worcester, MA USA}
        \item Developing a model-free reinforcement learning method for stochastic planning under temporal logic constraints using PyTorch.
        \item Using temporal logic formulas instead of reward function to rigorously express the desired properties to be achieved in the learned policies for stochastic systems. 
        \item Addressing the sparse reward issue for a stochastic dynamic system with partial observation. 
        \item Providing provable performance guarantees in the controller learned from RL algorithms.
\end{rSubsection} 

    \begin{rSubsection}{DARPA SI3-CMD}{Jan. 2019 - Aug. 2020}{Researcher}{Worcester MA USA}
        \item Collaborated with Scientific Systems Company Inc (SSCI) on the Serial Interactions in Imperfect Information Games Applied to Complex Military Decision Making (SI3-CMD).
        \item Developed a theoretical framework and Python-based software for deceptive planning.
        \item Achieved a higher probability of completing objectives by using asymmetrical information.
    \end{rSubsection}

    \begin{rSubsection}{DARPA Robotics Challenge}{Aug. 2014 - May 2015}{Researcher}{Worcester, MA USA}
        \item Collaborated with a team from Carnegie Mellon University on Atlas Humanoid robot.
        \item Developed a motion planner for arm manipulation using ROS, RVIZ, OpenRave, and Gazebo.
    \end{rSubsection}
\end{rSection}

%----------------------------------------------------------------------------------------
%	INDUSTRY EXPERIENCE SECTION
%----------------------------------------------------------------------------------------
\begin{rSection}{Industry Experience}
\begin{rSubsection}{Software Engineering Contractor}{Aug. 2015 - Jan. 2016}{Rudolph Technologies}{Tewksbury, MA USA}
\item Improved the code quality of a system that collects data from wafers. 
\item Analyzed and visualized data to help customers with improving CPU production.
\end{rSubsection}

\begin{rSubsection}{Software Engineering Intern}{Jun. 2015 - Aug. 2015}{Rudolph Technologies}{Tewksbury, MA USA}
\item Developed an automated tool for migrating codebase from multiple version control systems to a unified system.
\end{rSubsection}

\begin{rSubsection}{Software Engineering Intern}{Jul. 2013 - Aug. 2013}{Neusoft}{China}
\item Developed a map management system. 
\item Optimized the efficiency of inserting, deleting, editing operations over maps. 
\end{rSubsection}
\end{rSection}

%----------------------------------------------------------------------------------------
%	TEACHING EXPERIENCE SECTION
%----------------------------------------------------------------------------------------
\begin{rSection}{Teaching Experience}
\begin{rSubsection}
{Teaching Assistant}{Aug. 2020 - Present}{RBE 3001. \& 3002. Unified Robotics III \& IV, WPI}{Worcester, MA USA}
\item Led 3D-printed robot arm control lab and mobile robot navigation lab.
\item Designed and evaluated students' final projects, lab reports, and homework assignments.
\end{rSubsection}

\begin{rSubsection}{Teaching Assistant}{Aug. 2018 - Dec. 2018}{RBE 549. Computer Vision, WPI}{Worcester, MA USA}
\item Conducted a lecture on image filtering.
\item Led office hours to assist students in understanding course material and with homework difficulties.
\end{rSubsection}
\begin{rSubsection}{Teaching Assistant}{Aug. 2017 - May 2018}{RBE 1001. Introduction to Robotics, WPI}{Worcester, MA USA}
\item Supervised a team of 5 undergraduate peer learning assistants.
\item Mentored students and evaluated final projects, lab reports, and homework assignments.
\end{rSubsection}
\end{rSection}

%----------------------------------------------------------------------------------------
%	PUBLICATIONS SECTION
%----------------------------------------------------------------------------------------
\begin{rSection}{Publications}
    \begin{pSubsection}{Under review}{U}
        \item L.Li and J. Fu, "Policy Synthesis for Metric Interval Temporal Logic with Probabilistic Distributions", arXiv preprint arXiv:2105.04593, 2021
        \item \bibentry{li2020dynamic}
    \end{pSubsection}

    \begin{pSubsection}{Conference}{C}
        \item \bibentry{li2019topological}
        \item \bibentry{li2019approximate}
        \item \bibentry{li2017sampling}
        \item \bibentry{li2016birrtopt}
        \item \bibentry{atkeson2015no}
    \end{pSubsection}

    \begin{pSubsection}{Journal}{J}
        \item \bibentry{chen2018building}
        \item \bibentry{dedonato2017team}
        \item \bibentry{atkeson2016happened}
    \end{pSubsection}
    
    \begin{pSubsection}{Book}{B}
        \item \bibentry{atkeson2018achieving}
        \item \bibentry{atkeson2018happened}
    \end{pSubsection}

    \begin{pSubsection}{Thesis}{T}
        \item \bibentry{limaster}
        \item \bibentry{libs}
        \item \bibentry{liba}
    \end{pSubsection}
    
    \begin{pSubsection}{Presentation}{P}
        \item {Topological approximate dynamic programming under temporal logic constraints.} Poster Presentation, Northeast Robotics Colloquium (NERC), 2019.
        \item {Topological approximate dynamic programming under temporal logic constraints.} Poster Presentation, Robot Learning Workshop, 2019.
        \item {Approximate dynamic programming with probabilistic temporal logic constraints}, Paper Presentation, American Control Conference (ACC), 2019.
        \item {Sampling-based approximate optimal temporal logic planning}, Paper Presentation, IEEE International Conference on Robotics and Automation (ICRA), 2017
        \item {Birrtopt: A combined sampling and optimizing motion planner for humanoid robots} Poster Presentation, International Conference on Humanoid Robots (Humanoids), 2016.
        \item {Birrtopt: A combined sampling and optimizing motion planner for humanoid robots} Paper Presentation, Northeast Robotics Colloquium (NERC), 2016.
    \end{pSubsection}
\end{rSection}

%----------------------------------------------------------------------------------------
%	AWARDS SECTION
%----------------------------------------------------------------------------------------
\begin{rSection}{Honors \& Awards}
{\bf Summa Cum Laude} \hfill {Jul. 2014} \\
{\it Harbin Institute of Technology} \hfill {China}
    
{\bf Travel Grant Award, \$250} \hfill {Oct. 2019}\\
{\it Lehigh University}\hfill {Bethlehem, PA USA}

{\bf Graduate Student Travel Award, \$500} \hfill {Oct. 2019} \\
{\it Worcester Polytechnic Institute} \hfill {Worcester, MA USA}

{\bf Graduate Student Travel Award, \$400} \hfill {Mar. 2019} \\
{\it Worcester Polytechnic Institute}\hfill {Worcester, MA USA}

{\bf Graduate Student Travel Award, \$1000} \hfill {Jun. 2017}\\
{\it Worcester Polytechnic Institute}\hfill {Worcester, MA USA}
\end{rSection}


%----------------------------------------------------------------------------------------
%	EXTRACURRICULAR ACTIVITIES SECTION
%----------------------------------------------------------------------------------------
\begin{rSection}{Extracurricular Activities}
    \begin{rSubsection}{President}{Jan. 2019 - May 2020}{Graduate Student Government (GSG)}{Worcester, MA USA}
        \item Supervised the GSG governing body.
        \item Presented on behalf of the GSG to the university administration.
        \item Collaborated with Graduate Studies Office to raise awareness of housing issues to Board of Trustees.
        \item Chaired provost search committee and made recommendations. 
    \end{rSubsection}
    \begin{rSubsection}{Volunteer Teacher}{Jul. 2013 - Sep. 2013}{Lhasa Welfare Center for Children}{China}
        \item Fundraised for providing educational services to children from low-income families.
        \item Volunteered to educate children across different subjects, including Chinese, Math, and English.
\end{rSubsection}
\end{rSection}

%----------------------------------------------------------------------------------------
%	EDITORIAL ACTIVITIES SECTION
%----------------------------------------------------------------------------------------
\begin{rSection}{Editorial Activities}
    \begin{lSubsection}{Journal Reviewer}
        \item IEEE Control Systems Letters (L-CSS).   
    \end{lSubsection}
    \begin{lSubsection}{Conference Reviewer}
        \item International Conference on Robotics and Automation (ICRA) 2017 2021.
        \item American Control Conference (ACC), 2019 2021
        \item IEEE Conference on Decision and Control (CDC), 2018 2019 2020
        \item IEEE/RSJ International Conference on Intelligent Robots and Systems (IROS), 2020
        \item International Conference on Ubiquitous Robots (UR), 2020
    \end{lSubsection}
\end{rSection}

%----------------------------------------------------------------------------------------
%	LANGUAGE PROFICIENCY SECTION
%----------------------------------------------------------------------------------------
\begin{lSection}{Language Proficiency}
    \item {\bf Chinese}, Native
    \item {\bf English}, Fluent
\end{lSection}

%----------------------------------------------------------------------------------------
%	SKILLS SECTION
%----------------------------------------------------------------------------------------
\begin{rSection}{Skills}
    \begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
    Programming & C/C++, Python, MATLAB, Java, SQL, Assembly Language, LaTex, HTML \\
    Robotic Tools & ROS, RVIZ, Gazebo, OpenRave \\
    Software & PyTorch, Git, Vim, PowerBuilder \\
    Others & Ubuntu, VS Code, QtCreator, MFC, Perforce, Verilog
    \end{tabular}
\end{rSection}

%----------------------------------------------------------------------------------------
%	ORGANIZATION MEMBERSHIPS SECTION
%----------------------------------------------------------------------------------------
\begin{lSection}{Organization Memberships}
    \item {\bf Member}, IEEE
    \item {\bf Member}, IEEE Young Professionals
    \item {\bf Member}, IEEE Robotics and Automation Society
    \item {\bf Member}, Association for Women in Mathematics
\end{lSection}


\end{document}
